Papers

### 2024-02-23 papers.qmd
add slides for purdue

## Invited Talks
"Elasic Bayesian Model Calibration" *ASA SDNS Webinar*, December 04, 2023, [Slides](https://jdtuck.github.io/ASA_23_Calibration/index.html)

>>>>

## Invited Talks
"Bayesian Model Calibration: An Elastic Approach" *Purdue Statistical Colloquium*, February 23, 2024, [Slides](https://jdtuck.github.io/presentations/Purdue_Feb24/Purdue_Feb24.html)

"Elasic Bayesian Model Calibration" *ASA SDNS Webinar*, December 04, 2023, [Slides](https://jdtuck.github.io/presentations/ASA_23_Calibration/index.html)
